Explore expression of marker genes for tumor cell states

### 2025-01-14 analyses/cell-type-ewings/exploratory_analysis/06-tumor-cell-state-assignment.Rmd

`EWS-FLI1` low  - 2
`EWS-FLI1` middle - 1 & 4
`EWS-FLI1` high - 3

@@

`EWS-FLI1` low - 1
`EWS-FLI1` middle - 6 
`EWS-FLI1` high - 3, 4, 5, 7
`EWS-FLI1` high proliferative - 2

>>>>

- `EWS-FLI1` low  - 2
- `EWS-FLI1` middle - 1 & 4
- `EWS-FLI1` high - 3

@@

- `EWS-FLI1` low - 1
- `EWS-FLI1` middle - 6 
- `EWS-FLI1` high - 3, 4, 5, 7
- `EWS-FLI1` high proliferative - 2
